Standalone Tactics using OpenTheory

### 2012-02-13 paper.tex
minor tweaks

As an example, suppose the user of an interactive theorem prover faced with the goal
\[
\forall n.\ 8\le n\Rightarrow\exists s,t.\ n = 3s + 5t
\]
decides to pass it off to a standalone tactic for linear arithmetic.\footnote{This is a representation of the problem asking for a proof that \pounds 3 and \pounds 5 coins can be used to make \pounds $n$ for any natural number $n$ that is at least 8.}

@@

Requirements~\ref{req:artr} and \ref{req:artw} can be satisfied for an interactive theorem prover by implementing an \OpenTheory interface that can interpret and construct articles.
The central concept in \OpenTheory is that of a \emph{theory package}, $\theory{\Gamma}{\Delta}$, which proves that the set of theorems $\Delta$ logically derive from the set of assumptions $\Gamma$. An article is a concrete representation of a theory package, consisting of instructions for a virtual machine whose operations include construction of types, terms, and the primitive inference rules of higher order logic. To read an article, an interactive theorem prover performs the primitive inferences and other instructions listed in the file. The \OpenTheory logical kernel is based on HOL Light's logical kernel, and the instructions are chosen to make it easy to read articles into any system that can prove theorems of higher order logic.

@@

The main advantage to using \OpenTheory for communication is that it provides a standard, independent framework for fixing the meanings of constants between different systems.
For example, the numerals 3, 5 and 8 in the example goal term can be encoded in binary using the standard constants \texttt{Number.Natural.bit0} and \texttt{Number.Natural.bit1}.
The full names and properties of these constants are indicated in the \OpenTheory standard library, and interactive theorem provers can maintain translations to and from their local names and theorems.
A system using a different encoding for numbers (say unary, with \texttt{Number.Natural.suc} and \texttt{Number.Natural.zero}) could use additional standalone tactics to translate between encodings.

@@

\item\label{req:ckpt} A facility for check-pointing the proof assistant, or for extracting a standalone executable encompassing the tactic functionality.
\end{enumerate}

>>>>

As an example, suppose the user of an interactive theorem prover is faced with the goal
\[
\forall n.\ 8\le n\Rightarrow\exists s,t.\ n = 3s + 5t
\]
decides to pass it off to a standalone tactic for linear arithmetic.\footnote{This is a representation of the problem asking for a proof that \pounds 3 and \pounds 5 coins can be used to make \pounds $n$ for any natural number $n$ that is at least 8.}

@@

Requirements~\ref{req:artr} and \ref{req:artw} can be satisfied for an interactive theorem prover by implementing an \OpenTheory interface that can interpret and construct articles.
The central concept in \OpenTheory is that of a \emph{theory package}, $\theory{\Gamma}{\Delta}$, which proves that the set of theorems $\Delta$ logically derive from the set of assumptions $\Gamma$.
An article is a concrete representation of a theory package, consisting of instructions for a virtual machine whose operations include construction of types and terms, and the primitive inference rules of higher order logic.
To read an article, an interactive theorem prover performs the primitive inferences and other instructions listed in the file.
The \OpenTheory logical kernel is based on HOL Light's logical kernel, and the instructions are chosen to make it easy to read articles into any system that can prove theorems of higher order logic.

@@

The main advantage to using \OpenTheory for communication is that it provides a standard, independent framework for fixing the meanings of constants between different systems.
For example, the numerals $3$, $5$ and $8$ in the example goal term can be encoded in binary using the standard constants \texttt{Number.Natural.bit0} and \texttt{Number.Natural.bit1}.
The full names and properties of these constants are indicated in the \OpenTheory standard library, and interactive theorem provers can maintain translations to and from their local names and theorems.
A system using a different encoding for numbers (say unary, with \texttt{Number.Natural.suc} and \texttt{Number.Natural.zero}) could use additional standalone tactics to translate between encodings.

@@

\item\label{req:ckpt} A facility for checkpointing the proof assistant, or for extracting a standalone executable encompassing the tactic functionality.
\end{enumerate}
